EWJN from a BCS Superconductor

### 2021-01-26 paper.tex
adds title
Additional description of the nonlocal case vs local

\title{Title}

@@

The electromagnetic field fluctuations that contribute to qubit relaxation haven described in~\cite{QubitRelax} and~\cite{Henkel1999}.
Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations:
\begin{equation}
	\frac{1}{T_1} = \frac{d_{(E,B)}^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E,B)}(r, \omega) \coth\frac{\omega}{2 T}.
\end{equation}
Here, $\vec{d}_{(E,B)}$ is the dipole moment of a point qubit at position $\vec{r}$, with $i$ the direction of the qubit's dipole moment, with $(E,B)$ represents an electric or magnetic qubit (and correspondingly, an electric or magnetic spectral field density).
The frequency $\omega$ corresponds to the separation between energy levels of the qubit, and here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.

For a half space, these spectral densities can be written in terms of the surface's reflection coefficients, as derived by\cite{Henkel1999}.
Considering for now a qubit pointing in the direction perpendicular to the half-space, we can write
\begin{align}
	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u), \label{eq:chi}
\end{align}
with $z$ the distance to the qubit from the half-space measured in terms of the vacuum wavelength $\lambda = \flatfrac{c}{\omega}$.
The integration variable $u$ effectively represents a momentum in units of $\flatfrac{1}{\lambda}$, with $v = \sqrt{1 - u^2}$.
If $v \geq 1$, we take the positive square root $v = i \sqrt{u^2 - 1}$.
The magnetic spectral density is the same, except with an additional factor of $\flatfrac{1}{c^2}$ and with $r_s$ instead of $r_p$.

For the description of the behaviour of~\eqref{eq:chi} to remain accurate for small $z$, we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
\begin{align}
	r_p(u) &= \frac{\pi v - \zeta_p(u)}{\pi v + \zeta_p(u)} \\
	r_s(u) &= \frac{\zeta_s(u) - \frac{\pi}{v}}{\zeta_s(u) + \frac{\pi}{v}} \\
	\zeta_p(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\kappa^2} \left( \frac{y^2}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} + \frac{u^2}{\epsilon_(\frac{\omega}{c}\kappa, \omega)} \right) \label{eq:zp} \\
	\zeta_s(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} \label{eq:zs} \\
	\kappa^2 &= u^2 + y^2
\end{align}
The treatment in~\cite{QubitRelax} compares the difference between these expressions and the simpler Fresnel reflection coefficients.
In effect, using the Fresnel reflection coefficients for a metal for some constant conductivity corresponds to a local limit $u \rightarrow 0$.

>>>>

\title{EWJN from a BCS Superconductor}

@@

Physically, we are interested in the relaxation time of a qubit near the surface of the metal.
Sufficiently close to the metal, such that the separation between qubit and metal is much smaller than the shortest dimension of the metallic body, we can approximate the metal as a half space.
This defines a natural coordinate system, and we can allow the metal to take up all points with $z$-coordinate less than zero, extending to infinity in the $x$ and $y$ directions.

For a charge qubit with level separation $\omega$ and dipole moment $\vec{d}$, the relaxation rate $\frac{1}{T_1}$ depends on the qubit's distance from the surface $z$, as well as its orientation $i$.
The vacuum wavelength $\lambda = \frac{c}{\omega}$ is a natural unit for this distance $z$, so we wil measure $z$ in units of $\lambda$.
The electromagnetic field fluctuations that contribute to qubit relaxation have been described in~\cite{QubitRelax} and~\cite{Henkel1999}.
Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations, and obtain the following expression:
\begin{equation}
	\frac{1}{T_1} = \frac{d^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E)}(z, \omega) \coth\frac{\omega}{2 T}.
\end{equation}
\todo{All the Nam stuff is in Gaussian units, so should pick one unit system and stick with it.
Doesn't affect results so far, as \chi is unitless and only depends on quantities that are the same in SI / Gaussian.
Still bad though.}
Here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.

Similarly, for spin qubits with dipole moment $\vec{\mu}$, both~\cite{QubitRelax} and~\cite{Henkel1999} have a similar expression with a different spectral density expression:
\begin{equation}
	\frac{1}{T_1} = \frac{\mu^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(B)}(z, \omega) \coth\frac{\omega}{2 T}.
\end{equation}

The spectral densities are in general functions of the geometry and electrodynamic response of the metal object.
A standard limiting case for the response is that of local, linear electrodynamics, where the relationship between the electric displacement $\vec{D}$ and electric field $\vec{E}$ is a proportionality:
\begin{equation}
	\vec{D}(\vec{r}) = \epsilon \vec{E}(\vec{r})
\end{equation}
For a metal with conductivity $\sigma$, this dielectric function will typically have a large imaginary value as determined by the Drude expression in Gaussian units:
\begin{equation}
	\epsilon = 1 + i\frac{4 \pi \sigma}{\omega}
\end{equation}

For a half space, these spectral densities can be written in terms of the surface's reflection coefficients, as derived by\cite{Henkel1999} for local electrodynamics.
Considering for now a qubit pointing in the direction perpendicular to the half-space, we can write
\begin{align}
	\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u). \label{eq:chi}
\end{align}
The integration variable $u$ effectively represents a momentum in units of $\flatfrac{1}{\lambda}$, with $v = \sqrt{1 - u^2}$.
If $v \geq 1$, we take the positive square root $v = i \sqrt{u^2 - 1}$.
The magnetic spectral density is the same, except with an additional factor of $\flatfrac{1}{c^2}$ and with $r_s$ instead of $r_p$.
In the local limit, for dielectric constant $\epsilon$, the reflection coefficients will be the Fresnel $r_p$ and $r_s$:
\begin{align}
	r_p &= \frac{\epsilon v - \sqrt{\epsilon - u^2}}{\epsilon v + \sqrt{\epsilon - u^2}} \\
	r_s &= \frac{v - \sqrt{\epsilon - u^2}}{ v + \sqrt{\epsilon - u^2}}
\end{align}

However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
The divergence here stems from the unphysicality of local electrodynamics at very small scales;
within the electromagnetic coherence length of the metal the full response function defined by
\begin{equation}
	\vec{D}(\vec{r, t}) = \int \dd{r'} \dd{t'} \epsilon(r, r', t, t') \vec{E}(\vec{r', t'})
\end{equation}
becomes necessary.

We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so 
we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
\begin{align}
	r_p(u) &= \frac{\pi v - \zeta_p(u)}{\pi v + \zeta_p(u)} \\
	r_s(u) &= \frac{\zeta_s(u) - \frac{\pi}{v}}{\zeta_s(u) + \frac{\pi}{v}} \\
	\zeta_p(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\kappa^2} \left( \frac{y^2}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} + \frac{u^2}{\epsilon_(\frac{\omega}{c}\kappa, \omega)} \right) \label{eq:zp} \\
	\zeta_s(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} \label{eq:zs} \\
	\kappa^2 &= u^2 + y^2
\end{align}
The treatment in~\cite{QubitRelax} compares the difference between these expressions and the simpler Fresnel reflection coefficients.
In effect, using the Fresnel reflection coefficients for a metal for some constant conductivity corresponds to a local limit $u \rightarrow 0$.
